Get CRediT

### 2022-11-04 scripts/r/09_credit_taxonomy.Rmd
update credit taxonomy, format author list

```{r}
#| label: load-libs
library(googlesheets4)
library("xml2")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("forcats")
library("readr")
library("kableExtra")
```

@@

```{r}
#| label: identify-download

@@

```{r}
#| label: load-tidy-csv

@@

>>>>

```{r}
#| label: load-libs
library("googlesheets4")
library("xml2")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("forcats")
library("readr")
library("kableExtra")
```

@@

```{r}
#| label: identify-download
#| eval: false

@@

```{r}
#| label: load-tidy-csv
# Load data
all_data_temp <- read_csv("data/CRediT/MSA_tenzing_contribution.csv")

@@

```{r}
#| label: copy-author-list
#| eval: false
# Copy author list to the clipboard so it can be pasted in RR
contributors %>% 
  select(name) %>% 
  mutate(name = glue::glue("- name: {name}\n")) %>% 
  pull() %>% 
  clipr::write_clip() 
```
